My title

### 2024-11-04 paper/paper.qmd
Added models

library(tidyverse)
library(testthat)
library(arrow)
library(here)
library(rstanarm)
library(bayesplot)
library(gt)
library(kableExtra)

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| warning: false
#| label: SummaryStatisticsComparison
#| tbl-cap: Directly compares support percentages and sample sizes for Harris and Trump, showing central tendencies and variability in polling data for each candidate.

@@

# Create a visual table using kable
summary_table %>%
  kable("html", caption = "Summary Statistics for Key Variables Comparing Kamala Harris and Donald Trump") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Percentage Statistics" = 5, "Sample Size Statistics" = 2)) %>%
  column_spec(2:8, width = "2em")  # Adjust column width if necessary

>>>>

library(tidyverse)
library(testthat)
library(arrow)
library(here)
library(rstanarm)
library(bayesplot)
library(gt)
library(kableExtra)
library(knitr)
library(webshot2)

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: SummaryStatisticsComparison
#| tbl-cap: Directly compares support percentages and sample sizes for Harris and Trump, showing central tendencies and variability in polling data for each candidate.

@@

# Create a visual table using kable
summary_table %>%
  kable(caption = "Summary Statistics for Key Variables Comparing Kamala Harris and Donald Trump") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Percentage Statistics" = 5, "Sample Size Statistics" = 2)) %>%
  column_spec(2:8, width = "2em")  # Adjust column width if necessary
